### 2020-09-03 README.Rmd
update docs

```{r }
neon_store()
```

These will persist between sessions, so you only need to download once
or to retrieve updates. `neon_store()` can take arguments to filter by product
or pattern in table name, e.g. `neon_store(table = "brd")`.

@@

[The NEON API now rate-limits requests.](https://data.neonscience.org/data-api/rate-limiting/#api-tokens).
Using a personal token will increase the number of requests you can make.
See that link for directions on registering for a token.
Then pass this token in `.token` argument of `neon_download()`,
or for frequent use, add this token as  an environmental variable, `NEON_DATA`
to your local `.Renviron` file in your user's home directory.

`neon_download()` must first query each the API of eacn NEON site which collects
that product, for each month the product is collected.
(It would be much more efficient on the NEON server if the API could take
queries of the from `/data/<product>/<site>`, and pool the results, rather than
require each month of sampling separately!)

>>>>

```{r }
neon_index()
```

These will persist between sessions, so you only need to download once
or to retrieve updates. `neon_index()` can take arguments to filter by product
or pattern (regular expression) in table name, e.g. `neon_index(table = "brd")`.

@@

If `neon_download()` exceeds the API request limit (with or without the token),
`neonstore` will simply pause for the required amount of time to avoid 
rate-limit-based errors.

[The NEON API now rate-limits requests.](https://data.neonscience.org/data-api/rate-limiting/#api-tokens).
Using a personal token will increase the number of requests you can make before
encountering this delay.  See link for directions on registering for a token.
Then pass this token in `.token` argument of `neon_download()`,
or for frequent use, add this token as  an environmental variable, `NEON_DATA`
to your local `.Renviron` file in your user's home directory. 
`neon_download()` must first query each the API of each NEON site which collects
that product, for each month the product is collected.

(It would be much more efficient on the NEON server if the API could take
queries of the from `/data/<product>/<site>`, and pool the results, rather than
require each month of sampling separately!)
